---
title: "rfiglet"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rfiglet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
code_output <- function(x) {
  writeLines(c("```", x, "```"))
}
```

```{r, echo = FALSE, results = "asis"}
code_output(rfiglet::figlet("rfiglet!"))
```

rfiglet is a pure-R implementation of [FIGlet](https://en.wikipedia.org/wiki/FIGlet) (Frank, Ian and Glenn's letters) a classic system for creating text banners in many fonts.

The core of the package is the `rfiglet::figlet` function, which renders a string in a figlet font (by default `standard`)

```{r}
rfiglet::figlet("Hello world!")
```

There are `r length(rfiglet::figlet_font_list())` bundled fonts, representing the standard figlet font library

```{r}
rfiglet::figlet_font_list()
```

Pass the name of the font to `rfiglet::figlet` to use it

```{r}
rfiglet::figlet("Hello shadow!", font = "shadow")
```

## More fonts!

There are *many* more fonts available, and these can be downloaded by running

```{r, results = "hide"}
path <- rfiglet::figlet_download_fonts()
```

This will download all the extra fonts to wherever `RFIGLET_FONT_DIR` points, falling back on the cache directory `tools::R_user_dir("rfiglet", "data"` in R 4.0.0 or higher

```{r}
dir(path)
```

Once downloaded you can reference these fonts by name (i.e., filename without the extension)

```{r}
rfiglet::figlet("Extra!", font = "acrobatic.flf")
```

## Layout

Some degree of layout conrol is available via the arguments `justify` and `width`, powered by R's `strwrap` and `format` options. By default lines are broken at the width of your terminal (`getOption("width")`) but you can override this.

If a string is too long it will be wrapped to fit:

```{r}
rfiglet::figlet("A quick brown fox", width = 45)
```

You can align the fragments relative to each other using `justify`:

```{r}
rfiglet::figlet("A quick brown fox", width = 45, justify = "centre")
```

Or relative to the entire width by adding `absolute = TRUE`

```{r}
rfiglet::figlet("A quick brown fox", width = 45, justify = "centre",
                absolute = TRUE)
```

The latter option is more obvious with a longer width or shorter text

```{r}
rfiglet::figlet("right", justify = "right", absolute = TRUE)
```
